### 2016-03-01 metrics.tex
ready submit

Given such a metric, the FPF \cite{Gonzalez} approach to fuzzer taming \cite{PLDI13}
begins by selecting an arbitrary test case.   FPF then proceeds by selecting the test
case, of all unranked tests, that has the largest minimum distance
from all already ranked test cases, repeating this until all tests are
ranked.  In other words, FPF always chooses a test case that is as dissimilar as
possible from all previously chosen test cases, based on the \emph{closest
already chosen} test case.  FPF is boundedly close
to optimal under certain assumptions \cite{Gonzalez}.

>>>>

Given such a metric, FPF \cite{Gonzalez} fuzzer taming \cite{PLDI13}
begins by ranking as first an arbitrary test case.   FPF next ranks the test
case, of all unranked tests, that has the largest minimum distance
from all ranked test cases --- the test case most dissimilar by \emph{closest}
already ranked test --- until all tests are ranked.  FPF is boundedly close
to optimal under certain assumptions \cite{Gonzalez}.
